Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-17 main.tex
Added some new figures temporarily at the bottom of the paper.

>>>>

\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/alignment_mapping_old}
\caption{Old mapping of alignment parallelism onto cpu concurrency}
\label{fig:alignment_mapping_old}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/alignment_mapping_cpu}
\caption{Proposed mapping of alignment parallelism onto cpu concurrency}
\label{fig:alignment_mapping_cpu}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/alignment_mapping_gpu}
\caption{Proposed mapping of alignment parallelism onto gpu concurrency}
\label{fig:alignment_mapping_gpu}
\end{figure}
